Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-25 docs/google-research-awards-latam/main.tex
merge

The workflow described in Section~\ref{sec:design} is currently
functional. This section shows preliminary results obtained with our
infrastructure providing some evidence that finding bugs in JS runtime
engines is promising. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of a
month. For example, bug \# 6 was manifested by the JS code \CodeIn{var
  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
function that returns a primitive value identifying the target
object~\cite{valueof}. That function returns an empty string in the
original version of this code. The modified version of the code
returns a string representation of a null character (called
\CodeIn{NUL} in ascii).
The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
is equivalent to the expression \CodeIn{String.ToNumber(a.valueOf())}
that converts a string to a number, but if the string cannot be
converted, the expression should evaluate to NaN (Not a Number)
\cite{unary-plus}. For this case, all engines but Chakra evaluate the unary
plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}

So far, six of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that, with the exception of one case, all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any bug on SpiderMonkey and V8. Finally, it is
worth noting that six of the 13 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from six different open
source engines, including a total of \Fix{38.9K} test files.

>>>>

The workflow described in Section~\ref{sec:design} is currently
functional. This section shows preliminary results obtained with our
infrastructure providing some evidence that finding bugs in JS runtime
engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of a
month. For example, bug \# 6 was manifested by the JS code \CodeIn{var
  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
function that returns a primitive value identifying the target
object~\cite{valueof}. That function returns an empty string in the
original version of this code. The modified version of the code
returns a string representation of a null character (called
\CodeIn{NUL} in ascii).
The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
is equivalent to the expression \CodeIn{String.ToNumber(a.valueOf())}
that converts a string to a number, but if the string cannot be
converted, the expression should evaluate to NaN (Not a Number)
\cite{unary-plus}. For this case, all engines but Chakra evaluate the unary
plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
   \bottomrule     
  \end{tabular}
\end{wraptable}

So far, eight of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that, with the exception of one case, all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any bug on SpiderMonkey and V8. Finally, it is
worth noting that six of the 13 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from six different open
source engines, including a total of \Fix{38.9K} test files.
